### 2018-08-06 article.tex
LaTeX mistakes

\begin{proof}
For all gates $(f, g)$, if it exists a unique transformation $f \Rightarrow
  g$, then
\begin{align}
\catE(f, g) &= V(f \Rightarrow g) \in \mathbb{Q} \cr
&= V(f) \oplus V(g)^{-1}
\end{align}
otherwise we already have $\catE(f, g) = \top \in \mathbb{Q}$.
For all gates $f$, we know that there is a identity transformation $f
  \Rightarrow f$ and
\begin{align}
\catE(f, f) &= V(id_f) \cr
&= V(f \Rightarrow f)\cr
&= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
Finally, for all gates $(f, g, h)$ such that there exists $r: f \Rightarrow
  g$ and $s: g \Rightarrow h$ in $\catC$, then the homomorphism $V$ give us
\begin{align}
\catE(f, h) &= V(f \Rightarrow h) \cr
&= V(\alpha \circ \beta) \cr
&= V(\align) \oplus V(\beta) \cr
&= V(g \Rightarrow h) \oplus V(f \Rightarrow g) \cr
&= \catE(g, h) \oplus \catE(f, g)
\end{align}
If either $\alpha$ or $\beta$ doesn't exists in $\mathbb{P}$ then
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
become
\[\begin{matrix}
&\catE(b, c) \oplus \top &\succeq \top \cr
{\rm or~} &\top \oplus \catE(a, b) &\succeq \top \cr
{\rm or~} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}

>>>>

\begin{proof}
For all gates $(f, g)$, if it exists a unique transformation $f \Rightarrow
  g$, then
\begin{align}
\catE(f, g) &= V(f \Rightarrow g) \in \mathbb{Q} \cr
&= V(f) \oplus V(g)^{-1}
\end{align}
otherwise we already have $\catE(f, g) = \top \in \mathbb{Q}$.
For all gates $f$, we know that there is a identity transformation $f
  \Rightarrow f$ and
\begin{align}
\catE(f, f) &= V(id_f) \cr
&= V(f \Rightarrow f)\cr
&= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
Finally, for all gates $(f, g, h)$ such that there exists $\alpha: f \Rightarrow
  g$ and $\beta: g \Rightarrow h$ in $\mathbb{P}$, then the homomorphism $V$
    give us
\begin{align}
\catE(f, h) &= V(f \Rightarrow h) \cr
&= V(\alpha \circ \beta) \cr
&= V(\alpha) \oplus V(\beta) \cr
&= V(g \Rightarrow h) \oplus V(f \Rightarrow g) \cr
&= \catE(g, h) \oplus \catE(f, g)
\end{align}
If either $\alpha$ or $\beta$ doesn't exists in $\mathbb{P}$ then
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
become
\[\begin{matrix}
&\catE(b, c) \oplus \top &\succeq \top \cr
{\rm or~} &\top \oplus \catE(a, b) &\succeq \top \cr
{\rm or~} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}
